Andres Karjus

### 2019-03-01 index.Rmd
link to poster

- Entered [a video](https://www.youtube.com/watch?v=t8InfFEIINc) to Science Magazine's 11th [Dance Your Ph.D contest](https://www.sciencemag.org/projects/dance-your-phd). The idea is to explain your research topic to the general public though interpretive dance.

@@

- In 2018-2019 I'm helping my supervisor Prof. Kenny Smith carry out occasional language evolution workshops in primary schools around Edinburgh and neighbouring areas.
- Co-organized the bimonthly [Edinburgh Language Lunch](http://groups.inf.ed.ac.uk/langlunch/) during 2016-2018. 
- Co-organized the [Linguistics and English Language Postgraduate Conference](http://www.lel.ed.ac.uk/~pgc/) of 2017 in Edinburgh, the [Why Linguistics Conference](http://whylinguistics.ut.ee) (2015) and the [Graduate Conference on Areal Linguistics, Grammar and Contacts](http://arealling.ut.ee) (2012) in Tartu, Estonia.

>>>>

- Poster to be presented at the [Inaugural ISLE workshop](https://www.comparativelinguistics.uzh.ch/en/events/ISLE-inaugural-workshop.html), here is an online [version with interactive plots](https://andreskarjus.github.io/isle_poster).

@@

- In 2018-2019 I'm helping my supervisor Prof. Kenny Smith carry out occasional language evolution workshops in primary schools around Edinburgh and Lothian.
- Entered [a video](https://www.youtube.com/watch?v=t8InfFEIINc) to Science Magazine's 11th [Dance Your Ph.D contest](https://www.sciencemag.org/projects/dance-your-phd). The idea is to explain your research topic to the general public though interpretive dance. We didn't win but it was a fun one to do!
- Co-organized the bimonthly [Edinburgh Language Lunch](http://groups.inf.ed.ac.uk/langlunch/) during 2016-2018. 
- Co-organized the [Linguistics and English Language Postgraduate Conference](http://www.lel.ed.ac.uk/~pgc/) of 2017 in Edinburgh, the [Why Linguistics Conference](http://whylinguistics.ut.ee) (2015) and the [Graduate Conference on Areal Linguistics, Grammar and Contacts](http://arealling.ut.ee) (2012) in Tartu, Estonia.
